Indexing Variation Graphs\footnote{This work was supported by the Wellcome Trust grant [098051].}

### 2016-04-06 paper/paper.tex
Sketched the sections on text indexes and path indexes.

@@

>>>>

Suffix tree \cite{Weiner1973}, suffix array \cite{Manber1993}

BWT \cite{Burrows1994}, LF-mapping

FM-index \cite{Ferragina2005a}, find, locate, extract

LCP array \cite{Manber1993}, CST \cite{Sadakane2007}

XBW \cite{Ferragina2009b}, GCSA \cite{Siren2014}

@@

find the start nodes of paths with label matching the pattern

general difficulty: exponential growth
GCSA \cite{Siren2014}

k-mer indexes based on hash tables, sorted k-mers

similarities between k-mer indexes and de Bruijn graphs

using de Bruijn graphs as indexes; false positives
- string Y matches node with key X: X is a prefix of Y or Y is a prefix of X
- add values (pointers to start nodes) to each node
- valid for existence queries of length up to k+1 and locate queries of length up to k

Path graphs
- a generalization of DBG as a path index
- keys must be prefix-free
- k-index: has a node matching any k-path in the input graph
- edge condition: Y has predecessor with c -> edge (X, Y) if cY matches X
- k-equivalent: union of values for nodes matching X identical for all |X| <= k
- k-equivalent + edge condition: no false positives of length <= k; no false negatives

pruned de Bruijn graphs: merge nodes of DBG while keeping the path graph k-equivalent
